%!TEX root = Slic3r-Manual.tex
\section{Slic3r Support} % (fold)
\label{sec:slic3r_support}

\index{community support}
\index{Freenode}
\index{IRC}
\index{RepRap}
\index{forums}
\index{website}
\index{blog}

A variety of resources are available to provide support for Slic3r.
\subsection{Wiki and FAQ} % (fold)
\label{sub:wiki_and_faq}
The wiki provides up-to-date documentation, and a FAQ section which may help resolve any queries or issues.
\begin{itemize}
    \item \url{https://github.com/alexrj/Slic3r/wiki/Documentation}
    \item \url{https://github.com/alexrj/Slic3r/wiki/FAQ}
\end{itemize}
% subsection wiki_and_faq (end)

\subsection{Blog} % (fold)
\label{sub:blog}
Tips, hints and advice are published on the Slic3r blog.
\begin{itemize}
    \item \url{http://slic3r.org/blog}
\end{itemize}
% subsection blog (end)

\subsection{IRC} % (fold)
\label{sub:irc}

Found on the \texttt{irc.freenode.net} server, the following chat rooms are often filled with people who can provide real-time help:
\begin{itemize}
\item \texttt{\#reprap}: Highly active community of the RepRap project with many users of Slic3r.
\item \texttt{\#slic3r}: Slic3r chat room where Slic3r developers and users can give help.
\end{itemize}

% subsection irc (end)

\subsection{RepRap.org Forum} % (fold)
\label{sub:reprap_org_forum}


A dedicated forum for Slic3r exists in the RepRap forums.
\begin{itemize}
    \item \url{forums.reprap.org/list.php?263}
\end{itemize}

% subsection reprap_org_forum (end)

\subsection{Issue Tracker} % (fold)
\label{sub:issue_tracker}

If a bug may have been found in the software then an issue may be raised in the project issue tracker.

\begin{itemize}
    \item \url{github.com/alexrj/Slic3r/issues}
\end{itemize}

\textbf{Please} take the time to read through the existing issues to see whether the problem has already been submitted.  Also make sure that the problem is a bug in the application, support related questions should not be submitted.

If the bug appears to be unreported then please read the bug report guide before submitting: \url{https://github.com/alexrj/Slic3r/wiki/Quick-guide-to-writing-good-bug-reports}.

% subsection issue_tracker (end)

% section slic3r_support (end)